Differential Expression

### 2020-03-31 cmc-rnaseq-de/Differential-Expression.Rmd
error with inputs
fix factor vars and df to matrix

# Download CQN counts
CQN_ID = "syn21825509"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id")

@@

# Get covariates
COVAR_ID = "syn21825507"
ALL_USED_IDs = c(ALL_USED_IDs, COVAR_ID)
COVARIATES = downloadFile(COVAR_ID)

>>>>

# Download CQN counts
CQN_ID = "syn21825509"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id") %>% 
  data.matrix()

@@

# Get covariates
COVAR_ID = "syn21825507"
ALL_USED_IDs = c(ALL_USED_IDs, COVAR_ID)
COVARIATES = downloadFile(COVAR_ID) %>% 
  tibble::column_to_rownames(var = "SampleID")

FactorCovariates <- c("Individual_ID", "Reported_Gender", "Dx.Tissue")
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
